### 2020-10-20 thesis/thesis.tex
address comment 32
adress comment 34

Deriving insight from these contributions, multiple stakeholders have become mobilized to set connectivity conservation goals for the region. A number of Non-Governmental NGOs have designed corridor networks for their jurisdiction, with varying degrees of inputs from previous scientific work; these include Nature Action Québec (NAQ), Centre de la Nature du Mont Saint Hilaire (CDN), the Centre d'interprétation du milieu écologique du Haut-Richelieu (CIME), and Appalachian Corridors (CA). These associations are now beginning to work together to design science-driven connectivity conservation plans for the whole region, and are in need of science-based decision support tools. They are also concerned with the social acceptability of conservation, and with the resilience of their plans given expected future land use and climate change. \\ \vspace{2em}

@@

But, as we quoted from \cite{williamson_spatially_2018} above, this view tends to assume that stakeholders want to pursue rational and optimal designs in their approach to conservation. There is a tendency to take a single-faceted approach to the optimisation problem, focusing on the trade-off between food production and the support for biodiversity. An alternative way is through the lens of ecosystem services  \cite{bennett_changing_2017}. Ecosystem services refer to the diversity of benefits that ecosystems provide to, and the many ways in which they support, human systems. Specifically, the concept of “bright spots" has potential for guiding the discussion beyond dichotomies and single faceted approaches, by focusing on multifunctionality in agroecosystems. In a landscape, “bright spots” are areas exceeding expectations for goals, such as agro-ecological multifunctionality, biodiversity, or connectivity \citep{frei_bright_2018}. They show promise as a tool to identify levers of change, and guide stakeholder discussion. Indeed, an approach that focuses on identifying bright spots for the provision of those ecosystem services can be valuable to an interactive process of stakeholder engagement. They offer starting points to work with to design scenarios. They are concrete examples to reason around what bundles of ecosystem services are desirable (elements of SW) for the conservation of ecological connectivity and which types of governance is needed to work toward them (elements of IC). In our study region, this framework is already being tested: \cite{frei_bright_2018} identified bright, dark and average spots within Montérégie for both landscape multifunctionality and avian biodiversity. They showed important spatial properties of bright spots, for instance that they were “neither spatially congruent nor in conflict”. Connectivity could be fully integrated with this approach in two ways: first, it would be interesting to see if current bright spots are congruent with connectivity, in order to assess the mismatch between connectivity and other bundles of ecosystem services. One example is that of bee diversity which was found to be higher in connected habitats in Montérégie \citep{martins_complementary_2018}. Second, areas that are prioritized as important for connectivity under models such as the ones we developed in chapter 1 could be used in the identification of bright spots. \\

>>>>

Deriving insight from these contributions, multiple stakeholders have become mobilized to set connectivity conservation goals for the region. A number of Non-Governmental NGOs have designed corridor networks for their jurisdiction, with varying degrees of inputs from previous scientific work; these include Nature Action Québec (NAQ), Centre de la Nature du Mont Saint Hilaire (CDN), the Centre d'interprétation du milieu écologique du Haut-Richelieu (CIME), and Corridoes Appalachiens (CA). These associations are now beginning to work together to design science-driven connectivity conservation plans for the whole region, and are in need of science-based decision support tools. They are also concerned with the social acceptability of conservation, and with the resilience of their plans given expected future land use and climate change. \\ \vspace{2em}

@@

But, as we quoted from \cite{williamson_spatially_2018} above, this view tends to assume that stakeholders want to pursue rational and optimal designs in their approach to conservation. There is a tendency to take a single-faceted approach to the optimisation problem, focusing on the trade-off between food production and the support for biodiversity. An alternative way is through the lens of ecosystem services  \citep{bennett_changing_2017}. Ecosystem services refer to the diversity of benefits that ecosystems provide to, and the many ways in which they support, human systems. Specifically, the concept of “bright spots" has potential for guiding the discussion beyond dichotomies and single faceted approaches, by focusing on multifunctionality in agroecosystems. In a landscape, “bright spots” are areas exceeding expectations for goals, such as agro-ecological multifunctionality, biodiversity, or connectivity \citep{frei_bright_2018}. They show promise as a tool to identify levers of change, and guide stakeholder discussion. Indeed, an approach that focuses on identifying bright spots for the provision of those ecosystem services can be valuable to an interactive process of stakeholder engagement. They offer starting points to work with to design scenarios. They are concrete examples to reason around what bundles of ecosystem services are desirable (elements of SW) for the conservation of ecological connectivity and which types of governance is needed to work toward them (elements of IC). In our study region, this framework is already being tested: \cite{frei_bright_2018} identified bright, dark and average spots within Montérégie for both landscape multifunctionality and avian biodiversity. They showed important spatial properties of bright spots, for instance that they were “neither spatially congruent nor in conflict”. Connectivity could be fully integrated with this approach in two ways: first, it would be interesting to see if current bright spots are congruent with connectivity, in order to assess the mismatch between connectivity and other bundles of ecosystem services. One example is that of bee diversity which was found to be higher in connected habitats in Montérégie \citep{martins_complementary_2018}. Second, areas that are prioritized as important for connectivity under models such as the ones we developed in chapter 1 could be used in the identification of bright spots. \\
